---
title: "Community Call September 2024"
author: Simeon Ng
date: "`r Sys.Date()`"
format: html
---

```{r load}
load("community_call_sept_2024.RData")
```

# Sensors by Community

## Southcentral

**Soldotna** \| Quant 460 \| Deployed 05/13/2024

```{r pm25-soldotna}
plot_quant_pm25(soldotna_pm25, "Soldotna", cols = "#12436D")
```

-   More variance on weekends.

------------------------------------------------------------------------

**Ninilchik** \| Quant 461 \| Deployed 05/13/2024

```{r pm25-ninilchik}
plot_quant_pm25(ninilchik_pm25, "Ninilchik", cols = "#12436D")
```

-   More variance on weekends. Peak around noon.

------------------------------------------------------------------------

**Homer** \| Quant 464 \| Deployed 05/14/2024

```{r pm25-homer}
plot_quant_pm25(homer_pm25, "Homer", cols = "#12436D")
```

-   More variance on weekends. Small peaks in morning & evening.

------------------------------------------------------------------------

**Seward** \| Quant 465 \| Deployed 06/05/2024

```{r pm25-seward}
plot_quant_pm25(seward_pm25, "Seward", cols = "#12436D")
```

-   Peak on weekends. Peaks in evening.

## Southeast

**Ketchikan** \| Quant 449 \| Deployed 01/31/2024

```{r pm25-ketchikan}
plot_quant_pm25(ketchikan_pm25, "Ketchikan", cols = "#12436D")
```

-   August wildfire effect? Peaks in morning & evening.

------------------------------------------------------------------------

**Haines** \| Quant 450 \| Deployed 01/30/2024

```{r pm25-haines}
plot_quant_pm25(haines_pm25, "Haines", cols = "#12436D")
```

-   August wildfire effect? Consistent levels throughout week.

------------------------------------------------------------------------

**Wrangell** \| Quant 451 \| Deployed 02/01/2024

```{r pm25-wrangell}
plot_quant_pm25(wrangell_pm25, "Wrangell", cols = "#12436D")
```

-   August wildfire effect? Consistent levels throughout week.

------------------------------------------------------------------------

**Hoonah** \| Quant 452 \| Deployed 01/30/2024

```{r pm25-hoonah}
plot_quant_pm25(hoonah_pm25, "Hoonah", cols = "#12436D")
```

-   Not affected by wildfires as much? Consistent levels throughout week.

------------------------------------------------------------------------

**Skagway** \| Quant 453 \| Deployed 01/31/2024

```{r pm25-skagway}
plot_quant_pm25(skagway_pm25, "Skagway", cols = "#12436D")
```

-   August wildfire effect? Levels rising through winter into summer.

------------------------------------------------------------------------

**Sitka** \| Quant 454 \| Deployed 03/21/2024

```{r pm25-sitka}
plot_quant_pm25(sitka_pm25, "Sitka", cols = "#12436D")
```

-   Peaks in mornings & evenings.

------------------------------------------------------------------------

**Juneau 5th St** \| Quant 455 \| Deployed 01/29/2024

```{r pm25-jnu5th}
plot_quant_pm25(juneau_5th_pm25, "Juneau 5th St", cols = "#12436D")
```

-   August wildfire effect? Peaks in mornings & evenings. Slightly lower on weekdays.

------------------------------------------------------------------------

**Juneau Museum** \| Quant 456 \| Deployed 01/29/2024

```{r pm25-jnumus}
plot_quant_pm25(juneau_mus_pm25, "Juneau Museum", cols = "#12436D")
```

-   August wildfire effect. Peaks in mornings & evenings. Slightly lower on weekdays.
