---
title: "Community Call September 2024"
author: <a href="https://github.com/simeon-s-ng">Simeon Ng</a>
date: "`r Sys.Date()`"
format: 
  html:
    grid:
      body-width: 1800px
      gutter-width: 100px
server: shiny
---

*Data last updated: 09/04/2024* || [Project Github](https://github.com/simeon-s-ng/Community-Call-Sept-2024)

# Community Sensor Network Diurnal Comparisons

```{r, include=FALSE}
#| label: setup
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width = 15,
  fig.height = 10,
  comment = ''
)
```

```{r, include=FALSE}
#| label: libraries
library(tidyverse)
library(keyring)
library(openair)
library(akairmonitorr)
library(shinyWidgets)
library(bslib)
library(bsicons)
library(gt)
```

```{r, eval=FALSE}
#| label: installed-quants
quants <- read_csv("installs.csv", show_col_types = FALSE) |>
  filter(
    Status == "Installed", 
    Location != "Napaskiak",
    Location != "Bethel",
    Location != "Fairbanks – Ncore",
    Location != "Anchorage – Garden",
    Location != "Juneau – Floyd Dryden") |> 
  select(Location, 'Install Date', Notes) |>
  arrange(Location) |> 
  gt() |> 
  tab_header(
    title = "Alaska Community Quant Sensors Index"
  ) |> 
  tab_stubhead(label = "Location") |> 
  opt_interactive() |> 
  opt_stylize(style = 1, color = "blue")
```

```{r, eval=FALSE}
#| label: key
key <- key_get("aa_key")
```

```{r, eval=FALSE}
#| label: import-quant-southcentral-pm25
soldotna_pm25 <- query_agileweb(
  "Quant_MOD00460", "PM25", start = "2024-05-13T00:00:00", api_key =  key
) |> clean_pm25()
ninilchik_pm25 <- query_agileweb(
  "Quant_MOD00461", "PM25", start = "2024-05-13T00:00:00", api_key =  key
) |> clean_pm25()
ccsc_pm25 <- query_agileweb(
  "Quant_MOD00462", "PM25", start = "2024-06-18T00:00:00", api_key = key
) |> clean_pm25()
homer_pm25 <- query_agileweb(
  "Quant_MOD00464", "PM25", start = "2024-05-14T00:00:00", api_key =  key
) |> clean_pm25()
seward_pm25 <- query_agileweb(
  "Quant_MOD00465", "PM25", start = "2024-06-05T00:00:00", api_key = key
) |> clean_pm25()
talkeetna_pm25 <- query_agileweb(
  "Quant_MOD00467", "PM25", start = "2024-07-01T00:00:00", api_key = key
) |> clean_pm25()
biglake_pm25 <- query_agileweb(
  "Quant_MOD00468", "PM25", start = "2024-07-01T00:00:00", api_key = key
) |> clean_pm25()
kodiak_pm25 <- query_agileweb(
  "Quant_MOD00660", "PM25", start = "2024-07-02T00:00:00", api_key = key
) |> clean_pm25()
```

```{r, eval=FALSE}
#| label: import-quant-southeast-pm25
ketchikan_pm25 <- query_agileweb(
  "Quant_MOD00449", "PM25", start = "2024-01-31T00:00:00", api_key = key
) |> clean_pm25()
haines_pm25 <- query_agileweb(
  "Quant_MOD00450", "PM25", start = "2024-01-30T00:00:00", api_key = key
) |> clean_pm25()
wrangell_pm25 <- query_agileweb(
  "Quant_MOD00451", "PM25", start = "2024-02-01T00:00:00", api_key = key
) |> clean_pm25()
hoonah_pm25 <- query_agileweb(
  "Quant_MOD00452", "PM25", start = "2024-01-30T00:00:00", api_key = key
) |> clean_pm25()
skagway_pm25 <- query_agileweb(
  "Quant_MOD00453", "PM25", start = "2024-01-31T00:00:00", api_key = key
) |> clean_pm25()
sitka_pm25 <- query_agileweb(
  "Quant_MOD00454", "PM25", start = "2024-03-21T00:00:00", api_key = key
) |> clean_pm25()
juneau_5th_pm25 <- query_agileweb(
  "Quant_MOD00455", "PM25", start = "2024-01-29T00:00:00", api_key = key
) |> clean_pm25()
juneau_mus_pm25 <- query_agileweb(
  "Quant_MOD00456", "PM25", start = "2024-01-29T00:00:00", api_key = key
) |> clean_pm25()
```

```{r, eval=FALSE}
#| label: import-quant-interior-pm25
tok_pm25 <- query_agileweb(
  "Quant_MOD00444", "PM25", start = "2023-10-26T00:00:00", api_key = key
) |> clean_pm25()
badger_pm25 <- query_agileweb(
  "Quant_MOD00445", "PM25", start = "2024-03-21T00:00:00", api_key = key
) |> clean_pm25()
galena_pm25 <- query_agileweb(
  "Quant_MOD00446", "PM25", start = "2023-09-27T00:00:00", api_key = key
) |> clean_pm25()
delta_pm25 <- query_agileweb(
  "Quant_MOD00447", "PM25", start = "2023-11-02T00:00:00", api_key = key
) |> clean_pm25()
goldstream_pm25 <- query_agileweb(
  "Quant_MOD00448", "PM25", start = "2024-02-20T00:00:00", api_key = key
) |> clean_pm25()
denali_pm25 <- query_agileweb(
  "Quant_MOD00457", "PM25", start = "2024-06-12T00:00:00", api_key = key
) |> clean_pm25()
nome_pm25 <- query_agileweb(
  "Quant_MOD00654", "PM25", start = "2024-05-23T00:00:00", api_key = key
) |> clean_pm25()
kotzebue_pm25 <- query_agileweb(
  "Quant_MOD00662", "PM25", start = "2024-07-09T00:00:00", api_key = key
) |> clean_pm25()
```

```{r, eval=FALSE}
#| label: import-quant-permanent-pm25
anc_perm_pm25 <- query_agileweb(
  "Quant_MOD00471", "PM25", start = "2023-10-03T00:00:00", api_key = key
) |> clean_pm25()
fbx_perm_pm25 <- query_agileweb(
  "Quant_MOD00443", "PM25", start = "2023-11-20T00:00:00", api_key = key
) |> clean_pm25()
jnu_perm_pm25 <- query_agileweb(
  "Quant_MOD00665", "PM25", start = "2024-04-29T00:00:00", api_key = key
) |> clean_pm25()
```

```{r, eval=FALSE}
#| label: save
pm25_list <- list(
  "Badger" = badger_pm25,
  "Big Lake" = biglake_pm25,
  "Campbell Creek Science Center" = ccsc_pm25,
  "Delta Junction" = delta_pm25,
  "Denali NP" = denali_pm25,
  "Galena" = galena_pm25,
  "Goldstream" = goldstream_pm25,
  "Haines" = haines_pm25,
  "Homer" = homer_pm25,
  "Hoonah" = hoonah_pm25,
  "Juneau Museum" = juneau_mus_pm25,
  "Juneau 5th" = juneau_5th_pm25,
  "Ketchikan" = ketchikan_pm25,
  "Kodiak" = kodiak_pm25,
  "Kotzebue" = kotzebue_pm25,
  "Ninilchik" = ninilchik_pm25,
  "Nome" = nome_pm25,
  "Seward" = seward_pm25,
  "Sitka" = sitka_pm25,
  "Skagway" = skagway_pm25,
  "Soldotna" = soldotna_pm25,
  "Talkeetna" = talkeetna_pm25,
  "Tok" = tok_pm25,
  "Wrangell" = wrangell_pm25
)
rm(key)
save.image("community_call_sept_2024.RData")
```

```{r}
#| label: load-data
load("community_call_sept_2024.RData")
```

**Select** a sensor and a date range to see its diurnal plots.

- The **dark blue lines** represent the <u>median</u> PM2.5 concentration (y-axis) within the plots variation of time (x-axis).
- The **dark blue areas** above the median represent the <u>25th/75th percentiles</u> of PM2.5 concentration within the plots variation of time, while the **light blue areas** above and below the 25/75 represent the <u>upper and lower quartiles</u> respectively.

<details>
  <summary><b>Click Here</b> to see the Alaska Community Quant Sensors Index</summary>

```{r, echo=FALSE, eval=TRUE, results="markup"}
quants
```

</details>

```{r}
#| label: ui

fluidPage(
  tags$style(
    ".form-control {
      font-size: 14px;
      height: 40px
    }
    .input-daterange input {
      min-height: 40px
    }
    .form-control input {
      font-size: 14px
    }
    .input-group-addon.input-group-prepend.input-group-append span {
      height: 20px
    }
    "
  ),
  br(),
  # Select sensor input ----
  fluidRow(
    column(
      2,
      pickerInput(
        "pm25_L",
        "Select a sensor",
        choices = names(pm25_list),
        multiple = FALSE,
        selected = "Badger"
      )
    ),
    column(
      4,
      dateRangeInput(
        'dateRangeL',
        label = "Select a date range",
        start = "2023-10-26", end = Sys.Date(),
        separator = "-",
      )
    ),
    column(
      2,
      pickerInput(
        "pm25_R",
        "Select a sensor",
        choices = names(pm25_list),
        multiple = FALSE,
        selected = "Delta Junction"
      )
    ),
    column(
      4,
      dateRangeInput(
        'dateRangeR',
        label = "Select a date range",
        start = "2023-10-26", end = Sys.Date(),
        separator = "-"
      )
    ),
  ),
  # Output pm25 value cards ----
  # fluidRow(
  #   column(
  #     3,
  #     value_box(
  #       title = "Maximum Hourly PM2.5 Concentration",
  #       value = textOutput("pm25_max_L"),
  #       showcase = bs_icon("chevron-bar-up"),
  #       theme = "bg-gradient-blue-green",
  #       height = "150px"
  #     )
  #   ),
  #   column(
  #     3,
  #     value_box(
  #       title = "Hours over 9 µg/m³",
  #       value = textOutput("pm25_hours_L"),
  #       showcase = bs_icon("exclamation-triangle-fill"),
  #       theme = "warning",
  #       height = "150px"
  #     )
  #   ),
  #   column(
  #     3,
  #     value_box(
  #       title = "Maximum Hourly PM2.5 Concentration",
  #       value = textOutput("pm25_max_R"),
  #       showcase = bs_icon("chevron-bar-up"),
  #       theme = "bg-gradient-blue-green",
  #       height = "150px"
  #     )
  #   ),
  #   column(
  #     3,
  #     value_box(
  #       title = "Hours over 9 µg/m³",
  #       value = textOutput("pm25_hours_R"),
  #       showcase = bs_icon("exclamation-triangle-fill"),
  #       theme = "warning",
  #       height = "150px"
  #     )
  #   )
  # ),
  # Output day&hour diurnal plots ----
  fluidRow(
    column(
      6,
      plotOutput("pm25_plot_L")
    ),
    column(
      6,
      plotOutput("pm25_plot_R")
    )
  ),
  # Output month diurnal plots ----
  fluidRow(
    column(
      3,
      plotOutput("pm25_plot_L_month")
    ),
    column(
      3,
      plotOutput("pm25_plot_L_day")
    ),
  # Output day diurnal plots ----
    column(
      3,
      plotOutput("pm25_plot_R_month")
    ),
    column(
      3,
      plotOutput("pm25_plot_R_day")
    )
  )
)
```

```{r}
#| label: server
#| context: server
library(shiny)
library(tidyverse)
library(akairmonitorr)

load("community_call_sept_2024.RData")

# Reactive data ----

quant_max_L <- reactive({
  pm25_list[[input$pm25_L]] |> 
    filter(date >= input$dateRangeL[1], date <= input$dateRangeL[2]) |> 
    select(pm25) |> 
    max()
})

quant_max_R <- reactive({
  pm25_list[[input$pm25_R]] |> 
    filter(date >= input$dateRangeR[1], date <= input$dateRangeR[2]) |> 
    select(pm25) |> 
    max()
})

quant_hours_L <- reactive({
  pm25_list[[input$pm25_L]] |> 
    filter(
      pm25 >= 35, 
      date >= input$dateRangeL[1], 
      date <= input$dateRangeL[2]
    ) |> 
    summarise(n = n())
})

quant_hours_R <- reactive({
  pm25_list[[input$pm25_R]] |> 
    filter(
      pm25 >= 35,
      date >= input$dateRangeR[1],
      date <= input$dateRangeR[2]
    ) |> 
    summarise(n = n())
})

quant_plot_L <- reactive({
  plot_quant_pm25(
    filter(
      pm25_list[[input$pm25_L]], 
      date >= input$dateRangeL[1], 
      date <= input$dateRangeL[2]
    ),
    input$pm25_L,
    cols = "#12436D"
  )
})

quant_plot_R <- reactive({
  plot_quant_pm25(
    filter(
      pm25_list[[input$pm25_R]], 
      date >= input$dateRangeR[1], 
      date <= input$dateRangeR[2]
    ),
    input$pm25_R,
    cols = "#12436D"
  )
})

# Output value boxes ----

output$pm25_max_L <- renderText({
  paste0(quant_max_L(), " µg/m³")
})

output$pm25_max_R <- renderText({
  paste0(quant_max_R(), " µg/m³")
})

output$pm25_hours_L <- renderText({
  paste0(quant_hours_L(), " hours")
})

output$pm25_hours_R <- renderText({
  paste0(quant_hours_R(), " hours")
})

# Output left sensor ----

output$pm25_plot_L <- renderPlot({
  plot(quant_plot_L(), subset = "day.hour")
})

output$pm25_plot_L_month <- renderPlot({
  plot(quant_plot_L(), subset = "month")
})

output$pm25_plot_L_day <- renderPlot({
  plot(quant_plot_L(), subset = "day")
})

# Output Right Sensor ----

output$pm25_plot_R <- renderPlot({
  plot(quant_plot_R(), subset = "day.hour")
})

output$pm25_plot_R_month <- renderPlot({
  plot(quant_plot_R(), subset = "month")
})

output$pm25_plot_R_day <- renderPlot({
  plot(quant_plot_R(), subset = "day")
})
```

[Alaska Department of Environmental Conservation](https://dec.alaska.gov/) || [Air Monitoring & Quality Assurance](https://dec.alaska.gov/air/air-monitoring/)

---

## Sensors by Ecoregion
### Northern Southeast Alaska
```{r}
#| label: Northern Southeast Alaska
eco_haines <- haines_pm25 |> rename(Haines = pm25)
eco_hoonah <- hoonah_pm25 |> rename(Hoonah = pm25)
eco_skagway <- skagway_pm25 |> rename(Skagway = pm25)
eco_jnufifth <- juneau_5th_pm25 |> rename("Juneau 5th" = pm25)
eco_jnumuseum <- juneau_mus_pm25 |> rename("Juneau Museum" = pm25)

nse_sensors <- reduce(
  list(
    eco_jnufifth,
    eco_jnumuseum,
    eco_haines,
    eco_hoonah,
    eco_skagway
  ),
  left_join,
  by = "date"
) |> 
  timeVariation(
    pollutant = c("Juneau 5th", "Juneau Museum", "Haines", "Hoonah", "Skagway"),
    statistic = "median",
    ci = FALSE,
    normalise = FALSE,
    cols = "Set1",
    ylab = "PM25 (µg/m³)",
    main = expression(
      bold('Northern Southeast Alaska PM'[2.5]*' Median Concentrations | 01/30/2024 - 09/03/2024')
    ),
    sub = expression(bold("median")),
    fontsize = 14
  )
```

### Southern Southeast Alaska
```{r}
#| label: Southern Southeast Alaska
eco_ketchikan <- ketchikan_pm25 |> rename(Ketchikan = pm25)
eco_wrangell <- wrangell_pm25 |> rename(Wrangell = pm25)
eco_sitka <- sitka_pm25 |> rename(Sitka = pm25)

sse_sensors <- reduce(
  list(
    eco_ketchikan,
    eco_wrangell,
    eco_sitka
  ),
  left_join,
  by = "date"
) |> 
  timeVariation(
    pollutant = c("Ketchikan", "Wrangell", "Sitka"),
    statistic = "median",
    ci = FALSE,
    normalise = FALSE,
    cols = "Set1",
    ylab = "PM25 (µg/m³)",
    main = expression(
      bold('Southern Southeast Alaska PM'[2.5]*' Median Concentrations | 01/31/2024 - 09/03/2024')
    ),
    sub = expression(bold("median")),
    fontsize = 14
  )
```

### Southcentral Alaska
```{r}
#| label: Southcentral Alaska
eco_soldotna <- soldotna_pm25 |> rename(Soldotna = pm25)
eco_ninilchik <- ninilchik_pm25 |> rename(Ninilchik = pm25)
eco_homer <- homer_pm25 |> rename(Homer = pm25)
eco_seward <- seward_pm25 |> rename(Seward = pm25)

sc_sensors <- reduce(
  list(
    eco_soldotna,
    eco_ninilchik,
    eco_homer,
    eco_seward
  ),
  left_join,
  by = "date"
) |> 
  timeVariation(
    pollutant = c("Soldotna", "Ninilchik", "Homer", "Seward"),
    statistic = "median",
    ci = FALSE,
    normalise = FALSE,
    cols = "Set1",
    ylab = "PM25 (µg/m³)",
    main = expression(
      bold('Southcentral Alaska PM'[2.5]*' Median Concentrations | 05/13/2024 - 09/03/2024')
    ),
    sub = expression(bold("median")),
    fontsize = 14
  )
```

### Interior Alaska
```{r}
#| label: Interior Alaska
eco_tok <- tok_pm25 |> rename(Tok = pm25) |> filter(date >= "2023-11-01")
eco_delta <- delta_pm25 |> rename(Delta = pm25)
eco_goldstream <- goldstream_pm25 |> rename(Goldstream = pm25)
eco_galena <- galena_pm25 |> rename(Galena = pm25)

int_sensors <- reduce(
  list(
    eco_tok,
    eco_delta,
    eco_goldstream,
    eco_galena
  ),
  left_join,
  by = "date"
) |> 
  timeVariation(
    pollutant = c("Tok", "Delta", "Goldstream", "Galena"),
    statistic = "median",
    ci = FALSE,
    normalise = FALSE,
    cols = "Set1",
    ylab = expression('PM'[2.5]*' (µg/m³)'),
    main = expression(
      bold('Interior Alaska PM'[2.5]*' Median Concentrations | 10/27/2023 - 09/03/2024')
    ),
    sub = expression(bold("median")),
    fontsize = 14,
    auto.text = FALSE
  )
```